% This is an example of the `Acknowledgment' section.
% To generate the final document, run latex, build and quick build commands
% on the skeleton-thesis file (not this one)

\chapter*{Acknowledgment}\label{acknowledgment}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\vspace{7mm}

Where to begin? I am immensely thankful to so many in my life for helping me get here physically, emotionally, pyschologically, and spiritually. 
The entire graduate school experience has been much more than simply an intellectual journey for me. I have grown into someone entirely different than the person I started as in the fall of 2017. 
This dissertation will only in part cover the expanse of knowledge and achievement intellectually that has been gifted to me by life. 
On the other hand I feel I could write many other dissertations on the work done on my soul during my time here in Nashville. 
Then maybe write another dissertation on the how it all ties together in the sum of my personhood. 
I only want to communicate whats happened for me so the reader knows how much the people I dedicate this dissertation have done for me in my life overall.  

First I believe that God has brought me here. I believe the complexity and beauty of the world around us requites a loving and scientific God much like the people I admire in academics. 
I dedicate this dissertation to my God who is my friend who loves me unconditionally and understands the world through and through along with every soul on the planet. 
He understands justice and even evil and has chosen to place me here knowing the good would outweigh the pain and that life is worth living amidst it all and I thank God for it now.
He understands the entire nature of Electricity and Magnetism and left it here for us to discover, much like he leaves a lot of things here for us to figure out, like justice, war, the problem of evil, politics, etc.

I also want to dedicate this dissertation to my lovely wife. She is the light of my life and an inspiration to not only me but everyone she knows. Her encouragement has brought me through many days of considering quitting
graduate school. She has always believed in me and I wouldn't not be where I am now if she wasnt in my life. Particularly in my 3rd year of study she has encouraged me to continue on in my study and press on towards my goals
and to also be gracious to myself when I do not meet these goals.

My family 

Dr. Adam Anderson...
Dr. John Gore